Examining False Negatives

### 2023-04-01 EnvironmentalData/DrinkingWaterMetagenomes/building_env_data_viral_features_set_dw.Rmd
Updating figures.

## Merging
```{r}
viruses <- left_join(x=vs2_c, y=checkV, by = c("contig"))
viruses <- left_join(x=viruses, y=dvf_c, by = c("contig", "assembly"))
viruses <- left_join(x=viruses, y=vb_c, by = c("contig"))
viruses <- left_join(x=viruses, y=vs_c, by = c("contig"))
viruses <- left_join(x=viruses, y=kj_c, by = c("contig", "assembly"))
```

>>>>

## Merging
```{r}
viruses <- left_join(x=checkV, y=vs2_c, by = c("contig"))
viruses <- left_join(x=viruses, y=dvf_c, by = c("contig", "assembly"))
viruses <- left_join(x=viruses, y=vb_c, by = c("contig"))
viruses <- left_join(x=viruses, y=vs_c, by = c("contig"))
viruses <- left_join(x=viruses, y=kj_c, by = c("contig", "assembly"))
```

### 2023-04-01 TestingPipeline/Scripts/examining_false_positives-short_fragments.Rmd
Updating figures.

tuning_not_viral <- function(current_score, ins, 
                         include_tv_1=T,
                         include_tv_2=T,
                         include_tv_3=T,
                         include_tv_4=T,
                         include_tv_5=F) {
    # tuning addition
  if (include_tv_1) {
    current_score[(ins$checkv_host_genes>50) & !ins$provirus] <- 0
  }
  if (include_tv_2) {
    current_score[ins$checkv_viral_genes==0 & ins$checkv_host_genes>=1] <- current_score[ins$checkv_viral_genes==0 & ins$checkv_host_genes>=1] - 1
  }
  if (include_tv_3) {
    current_score[((ins$checkv_viral_genes*3) <= ins$checkv_host_genes) & !ins$provirus] <- current_score[((ins$checkv_viral_genes*3) <= ins$checkv_host_genes) & !ins$provirus] - 1
  }
  if (include_tv_4) {
    current_score[ins$checkv_length>500000 & ins$hallmark<=1] <- 0
  }

@@

>>>>

tuning_not_viral <- function(current_score, ins, 
                         include_tv_1=T,
                         include_tv_2=T,
                         include_tv_3=T,
                         include_tv_4=T,
                         include_tv_5=F) {
    # tuning removal
  if (include_tv_2) {
    current_score[ins$checkv_viral_genes==0 & ins$checkv_host_genes>=1] <- current_score[ins$checkv_viral_genes==0 & ins$checkv_host_genes>=1] - 1
  }
  if (include_tv_3) {
    current_score[((ins$checkv_viral_genes*3) <= ins$checkv_host_genes) & !ins$provirus] <- current_score[((ins$checkv_viral_genes*3) <= ins$checkv_host_genes) & !ins$provirus] - 1
  }

@@

  if (include_tv_1) {
    current_score[(ins$checkv_host_genes>50) & !ins$provirus] <- -3
  }

  if (include_tv_4) {
    current_score[ins$checkv_length>500000 & ins$hallmark<=1] <- -3
  }

### 2023-04-01 TestingPipeline/Scripts/examining_false_positives.Rmd
Updating figures.

```{r getting_viral_set_1}
getting_viral_set_1 <- function(input_seqs,
                                include_vibrant=FALSE, 
                                include_virsorter2=FALSE,
                                include_deepvirfinder=FALSE,
                                include_tuning_viral=FALSE,
                                tv_1=T, tv_2=T, tv_3=T, tv_4=T,
                                include_tuning_not_viral=FALSE,
                                ntv_1=T, ntv_2=T, ntv_3=T, ntv_4=T, ntv_5=F,
                                include_virsorter=FALSE) {

@@

```{r}
viruses$keep_score_high_MCC <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = T,
                                              include_virsorter2 = T,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = T,
                                              include_virsorter = T)
```

>>>>

```{r}
getting_viral_set_1 <- function(input_seqs,
                                include_vibrant=FALSE, 
                                include_virsorter2=FALSE,
                                include_deepvirfinder=FALSE,
                                include_tuning_viral=FALSE,
                                tv_1=T, tv_2=T, tv_3=T, tv_4=T,
                                include_tuning_not_viral=FALSE,
                                ntv_1=T, ntv_2=T, ntv_3=T, ntv_4=T, ntv_5=F,
                                include_virsorter=FALSE) {

@@

```{r}
viruses$keep_score_high_MCC <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = T,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = T,
                                              include_virsorter = F)
```
